\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[backend=biber, sorting=ydnt, style=ieee, dashed=false]{biblatex}
\AtEveryBibitem{\clearfield{note}}
\addbibresource{dmillard.bib}

\pagenumbering{gobble}

\begin{document}
\nocite{*}

\begin{center}
  {\huge \textbf{David Millard}}
\end{center}

\begin{center}
    \url{https://dmillard.github.io}
\end{center}

\vspace{1em}

Ph.D. Candidate \hfill Ronald Tutor Hall Room 426\\
Robotics Embedded Systems Lab \hfill 3710 McClintock Ave\\
Computer Science Department \hfill Los Angeles, CA 90089\\
University of Southern California \hfill \href{mailto:dmillard@usc.edu}{\nolinkurl{dmillard@usc.edu}}

\section*{Education}

\begin{description}
\item[University of Southern California]
    Los Angeles, California \hfill August 2018 - August 2023 (expected)\\
    Ph.D. Candidate, Department of Computer Science \hfill GPA 4.00/4.00\\
    Advised by Prof. Gaurav Sukhatme
    
\item[University of Georgia]
    Athens, Georgia \hfill August 2010 - May 2014\\
    Bachelor of Science, double major in Math and Computer Science \hfill GPA 3.94/4.00
\end{description}

\section*{Awards}
\begin{description}
\item[NASA Space Technology Research Fellowship]
    Four-year graduate fellowship, awarded for NSTRF proposal \emph{Interpretable Predictive Planning for Human-Robot Teams}

\item[Computer Science Outstanding Undergraduate with Distinction]
    University of Georgia. Awarded to the best student in the Computer Science department.
    
\item[Foundation Fellowship]
    The University of Georgia's top academic undergraduate four-year
    scholarship, awarded to approximately 20 students per class.
\end{description}

\printbibliography[title=Publications]

\section*{Work experience}

\begin{description}
\item[Google Brain (Robotics at Google)]
    New York, New York \hfill January 2020 - June 2020\\
    Research Intern, Robotics\\
    Research projects in differentiable physics simulation, with applications to indetification and control of robotic systems. Resulted in publication.

\item[Iron Ox]
    San Mateo, California \hfill May 2019 - August 2019\\
    Roboticist Intern, Robotics\\
    Designed and implemented software for kinodynamically limited trajectory optimziation for industrial arm planning in a robotic agriculture context.

\item[Robotics Embedded Systems Lab] University of Southern California \hfill August 2018 - \\
\emph{Graduate Research Assistant}

\item[X (formerly Google X)]
    Mountain View, California \hfill December 2015 - June 2018\\
    Software Engineer, Robotics\\
    Built perception systems for mobile base navigation\\
    Designed and developed sequence learning models for dynamic obstacle prediction and avoidance
    
\item[Microsoft Corporation]
    Redmond, Washington \hfill July 2014 - November 2015\\
    Software Development Engineer, Windows 10 Photos\\
    Developed photo viewer application served to millions of customers (C\#/C++)
\end{description}

\section*{Leadership}

\begin{description}

\item[GradAMP USC Mentorship Program] \hfill 2021-\\
Mentored undergraduates interested in research and graduate school during applications for internships and graduate programs.

\item[Greyhills Academy Robotics Pilot] Tuba City, Navajo Nation, Arizona
\hfill April 2018\\
With another Googler, organized and taught a two day robotics pilot course for students living in the Navajo nation.\\
Developed a continuing partnership between Google and Greyhills academy, and set the schedule for future collaboration.

\item[UGA Mathcounts Outreach] University of Georgia\\
\emph{President} \hfill August 2013 - May 2014\\
Coordinated board meetings and set organizational direction for a 200+ member student volunteer tutoring organization.\\
Expanded reach from 8 to 11 middle schools and increased focus on students in need.\\
\emph{Volunteer Coordinator} \hfill August 2012 - May 2013\\
Coordinated 200+ student volunteers at 8 local middle schools, distributing curriculum materials and establishing contact with school administrations.

\item[Free IT Athens] Athens, Georgia \hfill August 2009 - May 2014\\
\emph{Staff Member}\\
Trained volunteers in building computers and interacting with customers.\\
Taught classes in basic computer use to low-income Athens residents.

\end{description}

\end{document}
